Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
sim edit
some typographical & alignment fixes

\begin{align}
\label{eqn:sat_two_add_generator}
	\begin{split}
		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
		\geq 0, \epsilon \in \{0, 1\}\} \\
		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
	\end{split}
\end{align}

@@

\begin{align*}
	y_i x_j &- A_{i,j} y_{i - 1}w_j & \text{ so that } 4 \leq i \leq 5,3
	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
	y_4^2 &+ B_1 y_3 y_5 \\
	y_4y_5 &+ B_2 y_3^2 x_3 \\
	y_5^2 &+ B_3 y_3^2 x_4
\end{align*}

@@

\begin{cor}
\label{cor:raise-stacky-order}
Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}. Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
$$
e_i \begin{cases}
	= e_i' &\text{ if }i \notin J\\
	\leq e_i' &\text{ if } i \in J
\end{cases}$$
then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L).$
\end{cor}
\begin{proof}
For $t \leq i \leq r$, let $(\sx_i,\Delta, L_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx',\Delta,L),$ and having signature $(g; e_1, \ldots. e_{i-1}, e_i, e_i, \ldots, e_i; \delta).$ Let 
$J_i = \{i,\ldots, r\}.$ Note that $(\sx_0,L_0,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.

@@

\begin{proof}
Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
By Lemma ~\ref{lem:generation_5} and Proposition
~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta,
\halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-2}
 if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
~\ref{lem:sat-1} if $P_i $ is not a basepoint of $L'$. Note,
in the case $P$  is a not basepoint of $\halfcan'$, Equation
~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d
\geq 3$.

@@

To show that these generate all of $R'$, we need to show that all
$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
and $7 < d \leq 25$. Note that we can again use Max No ether's theorem
(taking saturation into account) to see that

@@

All such base cases satisfy all of the hypotheses of Theorem
~\ref{lem:raise-stacky-order} and their corresponding $R' := R(\sx',
\Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
$e' := \max(5, e_1', \ldots, e_r')$ with relations generated up to
degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
from induction using Lemma ~\ref{lem:raise-stacky-order}(b) and
Corollary ~ \ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
\halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
It also follows from induction on Lemma ~\ref{lem:raise-stacky-order}(c)
and ~\ref{cor:raise-stacky-order} that the relations are generated
up to degree $2e$. \todo{What does it mean to induct on the statements of two lemmas? Clarify this please.}
 \end{proof}

>>>>

\begin{align}
\label{eqn:sat_two_add_generator}
		\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
		\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
\end{align}

@@

\begin{align*}
	&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
	&y_4^2 + B_1 y_3 y_5 \\
	&y_4 y_5 + B_2 y_3^2 x_3 \\
	&y_5^2 + B_3 y_3^2 x_4
\end{align*}

@@

\begin{cor}
\label{cor:raise-stacky-order}
Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}. Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
\begin{align*}
	e_i	= e_i' \text{ if }i \notin J \\
	& e_i \leq e_i' &\text{ if } i \in J
\end{align*}

\noindent
then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L)$.
\end{cor}
\begin{proof}
For $t \leq i \leq r$, let $(\sx_i,\Delta, L_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx',\Delta,L),$ and having signature $(g; e_1, \ldots. e_{i-1}, e_i, e_i, \ldots, e_i; \delta).$ Let 
$J_i = \{i,\ldots, r\}.$ Note that $(\sx_0,L_0,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.

@@

\begin{proof}
Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X \sim 2 K_X + \Delta$.
By Lemma ~\ref{lem:generation_5} and Proposition
~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta,
\halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-2}
 if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
~\ref{lem:sat-1} if $P_i $ is not a basepoint of $L'$. Note,
in the case $P$  is a not basepoint of $\halfcan'$, Equation
~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d
\geq 3$.

@@

To show that these generate all of $R'$, we need to show that all
$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
(taking saturation into account) to see that

@@

All such base cases satisfy all of the hypotheses of Theorem
~\ref{lem:raise-stacky-order} and their corresponding $R' := R(\sx',
\Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
$e' := \max(5, e_1', \ldots, e_r')$ with relations generated up to
degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
from induction using Lemma ~\ref{lem:raise-stacky-order}(b) and
Corollary ~\ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
\halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
It also follows from induction on Lemma ~\ref{lem:raise-stacky-order}(c)
and ~\ref{cor:raise-stacky-order} that the relations are generated
up to degree $2e$. \todo{What does it mean to induct on the statements of two lemmas? Clarify this please.}
 \end{proof}
